figures?

### 2023-11-24 Updates/2023-11-17 figures_draft.Rmd
update patter

Top 10 models and all models coloured by type and showing if they include covariates or not. 
```{r model-type, fig.width=10}
top10_temp <- 
  temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |>
  slice_max(mean_crps, n= 10, na_rm = T) |>
  left_join(model_meta) |> 
  mutate(model_id = fct_reorder(model_id, mean_crps)) |> 
  ggplot(aes(x=mean_crps, y = model_id, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_NOAA)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", 
                   pattern_spacing = 0.02,
                   pattern_alpha = 0.5) + 
  scale_y_reordered() +
  labs(y='Model ID', x = 'mean CRPS skill (vs climatology)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw()

all_temperature <- temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(model_meta) |> 
  mutate(model_id = fct_reorder(model_id, mean_crps)) |> 
  ggplot(aes(x=mean_crps, y = model_id, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_NOAA)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", 
                   pattern_spacing = 0.02,
                   pattern_alpha = 0.8) + 
  scale_y_reordered() +
  labs(y='Model ID', x = 'mean CRPS skill (vs climatology)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw()

ggpubr::ggarrange(top10_temp, all_temperature, nrow = 1, 
                  common.legend = T,
                  legend = 'top', labels = 'auto')

>>>>

Top 10 models and all models coloured by type and showing if they include covariates or not. 
```{r model-type, fig.width=10}
top10_temp <- 
  temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |>
  slice_max(mean_crps, n= 10, na_rm = T) |>
  left_join(model_meta) |> 
  mutate(model_id = fct_reorder(model_id, mean_crps)) |> 
  ggplot(aes(x=mean_crps, y = model_id, fill = model_type)) +    # Different pattern for each group
  geom_bar_pattern(aes(pattern = as.factor(uses_NOAA)),
                   stat = "identity",
                   alpha = 0.8, 
                   pattern_fill = "black",
                   colour = "black", 
                   pattern_spacing = 0.04,
                   pattern_alpha = 1) + 
  scale_y_reordered() +
  labs(y='Model ID', x = 'mean CRPS skill (vs climatology)') +
  geom_vline(xintercept = 0) +
  scale_fill_manual(values = cols_modeltype) +
  scale_pattern_manual(values=c('none', 'stripe')) +
  scale_pattern_type_manual(values=c(NA, NA)) +
  theme_bw()  + 
    guides(pattern = guide_legend(override.aes = list(fill = "white")),
           fill = guide_legend(override.aes = list(pattern = "none")))

all_temp <- temperature_skill |> 
    group_by(model_id) |> 
    summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
    left_join(model_meta) |> 
    mutate(model_id = fct_reorder(model_id, mean_crps)) |> 
    ggplot(aes(x=mean_crps, y = model_id, fill = model_type)) +    # Different pattern for each group
    geom_bar_pattern(aes(pattern = as.factor(uses_NOAA)),
                     stat = "identity",
                     alpha = 0.8, 
                     pattern_fill = "black",
                     colour = "black", 
                     pattern_spacing = 0.03,
                     pattern_alpha = 1) + 
    scale_y_reordered() +
    labs(y='Model ID', x = 'mean CRPS skill (vs climatology)') +
    geom_vline(xintercept = 0) +
    scale_fill_manual(values = cols_modeltype) +
    scale_pattern_manual(values=c('none', 'stripe'), name = 'Uses weather covariates?') +
    scale_pattern_type_manual(values=c(NA, NA), name = 'Uses weather covariates?') +
    theme_bw() + 
    guides(pattern = guide_legend(override.aes = list(fill = "white")),
           fill = guide_legend(override.aes = list(pattern = "none")))

ggpubr::ggarrange(top10_temp, all_temp, nrow = 1, 
                  common.legend = T,
                  legend = 'top', labels = 'auto')
